Quality measure notes

### 2021-08-19 StateOfPractice/Ao-Report/11Introduction.tex
MI report - update ch 3 and more

\section{Scope}
\label{sec_scope}
According to Bankman \cite{Bankman2000}, MI software deals with six different basic problems, while Angenentet et al. \cite{Angenent2006} pointed out that four fundamental problems are solved by MI software. While both mentioned Segmentation, Registration, and Visualization of medical images, Bankman also included Enhancement, Quantification, and three functions for MI archiving and telemedicine systems (Compression, Storage, and Communication) \cite{Bankman2000}. On the other hand, Angenent's team included Simulation \cite{Angenent2006}. According to Wikipedia contributors \cite{enwiki:1034877594}, MI software has primary functions in categories Segmentation, Registration, Visualization (including the basic display, reformatted views, and 3D volume rendering), Statistical Analysis, and Image-based Physiological Modelling. As Kim et al. \cite{Kim2011} describe, the general steps of medical image analysis after obtaining digital data include Enhancement, Segmentation, Feature Extraction, Classification, and Interpretation. Besides the above major functions, some MI software provides supportive functions. For example, with Tool Kit (TK) libraries VTK \cite{SchroederEtAl2006} and ITK \cite{McCormick2014}, developers build software with Visualization and Analysis functions; Picture Archiving and Communication System (PACS) helps users to economically store and conveniently access images \cite{Choplin1992}.

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept
color=orange!40,
level 1/.append style={level distance=5cm,sibling angle=72},
level 2/.append style={level distance=3cm,sibling angle=90},
level 3/.style={level distance=2.3cm,sibling angle=90}]
\node{MI software}
child[concept color=teal!40] { node {Enhancement}}
child[concept color=teal!40] { node {Analysis}
    child[concept color=blue!30] { node {Registration}}
    child[concept color=blue!30,] { node {Segmentation}}
    child[concept color=blue!30] { node {Statistical Analysis}
    child[concept color=blue!20] { node {Feature Extraction}}
    child[concept color=blue!20] { node {Classification}}
    child[concept color=blue!20] { node {Interpretation}}
    }}
child[concept color=teal!40] { node {Simulation/\\Modeling}}
child[concept color=teal!40] { node {Supporting}
    child[concept color=blue!30] { node {TK}}
    child[concept color=blue!30] { node {PACS}}
}
child[concept color=teal!40] { node {Visualization}
    child[concept color=blue!30] { node {2D Display}}
    child[concept color=blue!30] { node {3D Rendering}}
    child[concept color=blue!30] { node {Reformatted Views}}
};
\end{tikzpicture}
\caption{Major functions of MI software}
\label{fig_mi_functions}
\end{figure}

>>>>

\section{Scope}
\label{sec_scope}
According to Bankman \cite{Bankman2000}, MI software deals with six different basic problems, while Angenentet et al. \cite{Angenent2006} pointed out that four fundamental problems are solved by MI software. While both mentioned Segmentation, Registration, and Visualization of medical images, Bankman also included Enhancement, Quantification, and three functions for MI archiving and telemedicine systems (Compression, Storage, and Communication) \cite{Bankman2000}. On the other hand, Angenent's team included Simulation \cite{Angenent2006}. According to Wikipedia contributors \cite{enwiki:1034877594}, MI software has primary functions in categories Segmentation, Registration, Visualization (including the basic display, reformatted views, and 3D volume rendering), Statistical Analysis, and Image-based Physiological Modelling. As Kim et al. \cite{Kim2011} describe, the general steps of medical image analysis after obtaining digital data include Enhancement, Segmentation, Feature Extraction, Classification, and Interpretation. Besides the above major functions, some MI software provides supportive functions. For example, with Tool Kit libraries VTK \cite{SchroederEtAl2006} and ITK \cite{McCormick2014}, developers build software with Visualization and Analysis functions; Picture Archiving and Communication System (PACS) helps users to economically store and conveniently access images \cite{Choplin1992}.

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept
color=orange!40,
level 1/.append style={level distance=5cm,sibling angle=72},
level 2/.append style={level distance=3cm,sibling angle=90},
level 3/.style={level distance=2.3cm,sibling angle=90}]
\node{MI software}
child[concept color=teal!40] { node {Enhancement}}
child[concept color=teal!40] { node {Analysis}
    child[concept color=blue!30] { node {Registration}}
    child[concept color=blue!30,] { node {Segmentation}}
    child[concept color=blue!30] { node {Statistical Analysis}
    child[concept color=blue!20] { node {Feature Extraction}}
    child[concept color=blue!20] { node {Classification}}
    child[concept color=blue!20] { node {Interpretation}}
    }}
child[concept color=teal!40] { node {Simulation/\\Modeling}}
child[concept color=teal!40] { node {Supporting}
    child[concept color=blue!30] { node {Tool Kit}}
    child[concept color=blue!30] { node {PACS}}
}
child[concept color=teal!40] { node {Visualization}
    child[concept color=blue!30] { node {2D Display}}
    child[concept color=blue!30] { node {3D Rendering}}
    child[concept color=blue!30] { node {Reformatted Views}}
};
\end{tikzpicture}
\caption{Major functions of MI software}
\label{fig_mi_functions}
\end{figure}

### 2021-08-19 StateOfPractice/Ao-Report/12Background.tex
MI report - update ch 3 and more

	\item \textbf{Reliability} The probability of failure-free operation of a computer program in a specified environment for a specified time, i.e. the average time interval between two failures also known as the mean time to failure (MTTF) \cite{musa1987software} 
	\cite{GhezziEtAl2003}.

>>>>

	\item \textbf{Reliability} The probability of failure-free operation of a computer program in a specified environment for a specified time, i.e., the average time interval between two failures also known as the mean time to failure (MTTF) \cite{musa1987software} 
	\cite{GhezziEtAl2003}.

### 2021-08-19 StateOfPractice/Ao-Report/13Methods.tex
MI report - update ch 3 and more

We designed a general process for evaluating the state of the practice of domain-specific software, that we instantiate to SC software for a specific scientific domain.

Our method involves several steps, shown as follows:
\begin{enumerate}
\item choosing a software domain (Section \ref{sec_domain_selection});
\item collecting and filtering software packages (Section \ref{sec_software_selection});
\item grading the selected software (Section \ref{sec_grading_software});
\item interviewing development teams for further information (Section \ref{sec_interview_methods}).
\end{enumerate}

Section \ref{sec_applying_method} presents an example of how we applied the method on the MI domain.

\section{Domain Selection}
\label{sec_domain_selection}
Our methods are generic, but we have only applied them to scientific domains due to the objective of our research.

When choosing a candidate domain, we prefer one with a large number of active OSS. The reason is that we aim to finalize a list of 30 software packages \cite{SmithEtAl2021} after the screening step. For example, we remove the ones without recent updates or specific functions. Thus, we need enough software candidates from the beginning. Besides, we prefer OSS projects because our grading method requires access to the code. In addition, we prefer a domain with an active community developing and using the software. As a result, it is easier to invite enough developers for interviews.

@@

The process of selecting software packages contains two steps: i) identify software candidates in the chosen domain, ii) filter the list according to needs \cite{SmithEtAl2021}.

@@

The other filters are optional, and we consider them according to the number of software candidates and the objectives of the research project. We try to apply them in the following priority order:

\begin{enumerate}
\item The functions and purpose of the software. For example, we can choose a group of software with similar functions, so that the comparison is between the software; or we can cross-compare sub-groups in the domain, then we need to select candidates from each sub-group.

@@

\item The age of software. Some of the OSS projects may experience a lack of recent maintenance. So we eliminate packages without recent updates, unless they are still popular and highly recommended by the domain users \cite{SmithEtAl2021}. We consider a software project as ``alive" if it has any update within the last 18 months; otherwise, we mark it as ``dead".
\end{enumerate}

@@

\subsection{Vet the Software List}
\label{sec_vet_software_list}
Before showing our filtered list to the domain experts, we ask them to list the top 10 software in the domain. Then, we cross-compare the two lists and discuss the commons and differences.  In addition, we ask them to vet our filtered list. They provide opinions on whether the list is reasonable to them. We also value their opinions on the filtering process. For example, if a software package is not OSS and has no updates for a long while, but the domain experts identify it as a valuable product, we still consider it to keep.

@@

We use the first section of the template to collect general information, such as the name, purpose, platform, programming language, publications about the software, the first release and the most recent change date, website, and source code repository of the product, etc. Information in this section helps us understand the projects better and may be helpful for further analysis, but it does not directly affect the grading scores.

We designed the following nine sections in the template for the nine software qualities mentioned in Section \ref{sec_software_quality}. For each quality, we ask several questions and the typical answers are among the collection of ``yes'', ``no'', ``n/a'', ``unclear'', a number, a string, a date, a set of strings, etc. Each quality needs an overall score between 1 and 10 based on all the previous questions. For some qualities, we perform surface measurements, which allow us to carry out on all packages with reasonable efforts. The surface measurements reveal some traits of a underlying quality, but may not fully represent it.

\begin{itemize}
\item \textbf{Installability} We check the existence and quality of installation instructions. The user experience is also an important factor, such as the ease to follow the instructions, number of steps, automation tools, and the prerequisite steps for the installation. If any problem interrupts the process of installation or uninstallation, we give a lower score to this quality. We also record the operating system (OS) for the installation test and whether we can verify the installation.

@@

\item \textbf{Surface Reliability} We check that whether the software break during the installations and tutorials, whether there are descriptive error messages, and if we can recover the process after the errors.

\item \textbf{Surface Robustness} We check that how the software handle unexpected/unanticipated input. For example, for software packages with the function to load image files, we prepare broken image files for them to open. We use a text file (.txt) with a modified extension name (.dcm) as an unexpected/unanticipated input. We load a few correct input files to ensure the function is working correctly before testing with the unexpected/unanticipated ones.

\item \textbf{Surface Usability} We examine the documents of the projects and consider software with a getting started tutorial and a user manual easier to use. Meanwhile, we check if users have any channels to get supports. Our impressions and user experiences when testing the software also affect the scores. For example, easy-to-use graphical user interfaces give us a better experience, thus lead to better scores.

@@

\item \textbf{reusability} We count the total number of code files for each project. Projects with a large number of components provide more choices to reuse. Furthermore, well-modularized code, which tends to have smaller parts in separated files, is easier to reuse. Thus, we consider the projects with more code files to be more reusable. We use \textit{GitStats} as a tool to count the number of text-based files for all projects, and consider the projects with more text-based files to also have more code files. We also decide that the projects with API documentation can deliver better \textit{Reusability}.

@@

\item \textbf{Visibility/Transparency} To measure this quality, such as all of the steps of a software development process and the current status of a project, we check the existing documents. We examine the development process, current status, development environment, and release notes for each project. If any information is missing or poorly conveyed, the \textit{visibility/transparency} is not ideal.
\end{itemize}

All the last three sections are about the empirical measurements. For some qualities, the empirical measurements also affect the score. We use tools to extract information from the source code repositories. For projects held on GitHub, we manually collect additional metrics, such as the stars of the GitHub repository, and the numbers of open and closed pull requests. Section \ref{sec_empirical_measurements} presents more details about the empirical measurements.

@@

We use two command-line tools for the empirical measurements. One is \textit{GitStats} that generates statistics for git repositories and display outputs in the format of web pages \cite{Gieniusz2019}; the other one is Sloc Cloc and Code (as known as \textit{scc}) \cite{Boyter2021}, aiming to count the lines of code, comments, etc.

@@

Additionally, we manually collect information for projects held on GitHub, such as the numbers of stars, forks, people watching this repository, open pull requests, closed pull requests, number of months a repository has been on GitHub. A git repository can have a creation date much earlier than the first day on GitHub. For example, the developers created the git repository of \textit{3D Slicer} in 2002, but did not upload a copy of it to GitHub until 2020. We get the creation date of the GitHub copy by using API \textit{https://api.github.com/repos/{:owner}/{:repository}} (e.g., \hyperlink{https://api.github.com/repos/slicer/slicer}{https://api.github.com/repos/slicer/slicer}). In the response, the value of ``created\_at" is what we want. The number of months a repository has been on GitHub helps us understand the average change of metrics over time, e.g., the average new stars per month.

@@

\subsection{Technical Details}
\label{sec_technical_details}
To test the software on a ``clean'' system, we create a new virtual machine (VM) for each software and only install the necessary dependencies before measuring. We make all 30 VM on the same computer, one at a time, and destroy them after measuring.

@@

The interviews are semi-structured based on the question list, and we also ask follow-up questions when necessary. Based on our experience, the interviewees usually bring up some exciting ideas that we do not expect, and it is worth expanding on these topics.

@@

Ideally, we select projects after the grading measurements and prefer the ones with higher overall scores. However, if we do not find enough participants, we contact all teams on the list.

@@

\subsection{Domain Selection}
Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the sub-group of software with the Visualization function shown in Figure \ref{fig_mi_functions}. We also included Dr. Michael Noseworthy and some of his students as the MI domain experts in our team.

\subsection{Software Product Selection}
\label{sec_mi_software_selection}
By using the method in Section \ref{sec_identify_software_candidates}, we identified 48 MI software projects as the candidates from publications \cite{Bjorn2017} \cite{Bruhschwein2019} \cite{Haak2015}, online articles related to the domain \cite{Emms2019} \cite{Hasan2020} \cite{Mu2019}, forum discussions related to the domain \cite{Samala2014}, etc. Appendix \ref{ap_list_before_filtering} shows all the 48 software packages.

@@

\begin{enumerate}
\item Among them, there were eight ones that we could not find their source code, such as \textit{MicroDicom}, \textit{Aliza}, and \textit{jivex}. These packages are likely to be freeware defined in Section \ref{sec_freeware} and not OSS. So following guidelines in Section \ref{sec_filter_software_list} we removed them from the list.

\item Next, we focused on the MI software providing visualization functions, as described in Section \ref{sec_scope}. Seven of the software on the list were tool kits or libraries for other software to use as dependencies, but not for end-users to view medical images, such as \textit{VTK}, \textit{ITK}, and \textit{dcm4che}; another three were PACS. We also eliminated these from the list.

@@

Following the process in Section \ref{sec_vet_software_list}, our domain experts provided a list of top software that contains 12 software products (Table \ref{tab_top_software_experts}). We compared two lists and found six common ones. We did not include the rest in our final list, because their major function was not Visualization.

@@

After vetting our filtered list, the domain experts believed it was reasonable and did not identify any problem. Thus, as shown in Appendix \ref{ap_list_before_filtering}, eventually we had 29 software products on the final list.

@@

\subsection{Interviews}
We received ethics clearance from the McMaster University Research Ethics Board (Appendix \ref{ap_ethics}). Going through the interview process in Section \ref{sec_interview_methods}, we contacted all of the 29 teams. As a result, developers/architects from 8 teams have participated in our interviews so far.

>>>>

We designed a general process for evaluating the state of the practice of domain-specific SC software, that we instantiate for a specific scientific domain.

Our method involves four steps:
\begin{enumerate}
\item choosing a software domain (Section \ref{sec_domain_selection});
\item collecting and filtering software packages (Section \ref{sec_software_selection});
\item grading the selected software (Section \ref{sec_grading_software});
\item interviewing development teams for further information (Section \ref{sec_interview_methods}).
\end{enumerate}

\noindent Section \ref{sec_applying_method} presents an example of how we applied the method on the MI domain.

\section{Domain Selection}
\label{sec_domain_selection}
Our methods are generic for any SC software, but they need to be applied to a specific domain. When choosing a candidate domain, we prefer one with a large number of active OSS. The reason is that we aim to finalize a list of 30 software packages \cite{SmithEtAl2021} after the screening step. For example, we remove the ones without recent updates or specific functions. Besides, we prefer OSS projects because our grading method requires access to the code. In addition, we prefer a domain with an active community developing and using the software. As a result, it is easier to invite enough developers for interviews.

@@

The process of selecting software packages contains two steps: i) identify software candidates in the chosen domain, ii) filter the list according to our needs \cite{SmithEtAl2021}.

@@

The other filters are optional, and we consider them according to the number of software candidates and the objectives of the research project. We apply them in the following priority order:

\begin{enumerate}
\item The functions and purpose of the software. An SC domain often contains software with various functions and purposes. For example, some MI software packages are Tool Kit for developers to use, and some others offer Visualization function to end-users. We have two options:
\begin{itemize}
\item selecting a set of software with the same major function. In this case, we can use the identical process to assess all packages, e.g., same input to measure \textit{Robustness}. Also, when we give impression scores to qualities such as \textit{Installability} and \textit{Usability}, the results are more comparable. Thus, it is more feasible to collect the results and rank the software.
\item selecting software from a set of different sub-groups. For example, we can choose 10 MI software from each of the three sub-groups: Visualization, Tool Kit, and PACS. The downside: we may need different processes to measure each sub-group; it may be less accurate to mix all three sub-groups and rank them together. The benefit: we can cross-compare the development processes between the sub-groups.
\end{itemize}

@@

\item The age of the software. Some of the OSS projects may experience a lack of recent maintenance. So we eliminate packages without recent updates, unless they are still popular and highly recommended by the domain users \cite{SmithEtAl2021}. We consider a software project as ``alive" if it has any update within the last 18 months; otherwise, we mark it as ``dead".
\end{enumerate}

@@

\subsection{Vet the Software List}
\label{sec_vet_software_list}
Before showing our filtered list to the domain experts, we ask them to list their top 10 software in the domain. Then, we cross-compare the two lists and discuss the commonality and variability.  In addition, we ask them to vet our filtered list. They provide views on whether the list is reasonable. We also use their opinions for a filtering process. For example, if a software package is not OSS and has had no updates for a long time, but the domain experts identify it as a valuable product, we still consider it in our final list.

@@

We use the first section of the template to collect general information, such as the name, purpose, platform, programming language, publications about the software, the first release and the most recent change date, website, source code repository of the product, etc. Information in this section helps us understand the projects better and may be helpful for further analysis, but it does not directly affect the grading scores.

We designed the following nine sections in the template for the nine software qualities mentioned in Section \ref{sec_software_quality}. For each quality, we ask several questions and the typical answers are among the collection of ``yes'', ``no'', ``n/a'', ``unclear'', a number, a string, a date, a set of strings, etc. Each quality needs an overall score between 1 and 10 based on all the previous questions. For some qualities, we perform surface measurements, which allow us to measure all packages with reasonable efforts. The surface measurements reveal some traits of a underlying quality, but may not fully represent it.

\begin{itemize}
\item \textbf{Installability} We check the existence and quality of installation instructions. The user experience is also an important factor, such as the ease to follow the instructions, number of steps, automation tools, and the prerequisite steps for the installation. If any problem interrupts the process of installation or uninstallation, we give a lower score to this quality. We also record the Operating System (OS) for the installation test and whether we can verify the installation.

@@

\item \textbf{Surface Reliability} We check whether the software breaks during the installations and tutorials, whether there are descriptive error messages, and if we can recover the process after an error.

\item \textbf{Surface Robustness} We check how the software handles unexpected/unanticipated input. For example, we prepare broken image files for software packages with the function to load image files. We use a text file (.txt) with a modified extension name (.dcm) as an unexpected/unanticipated input. We load a few correct input files to ensure the function is working correctly before testing with the unexpected/unanticipated ones.

\item \textbf{Surface Usability} We examine the documentation of the projects, and we consider software with a getting started tutorial and a user manual easier to use. Meanwhile, we check if users have any channels to get support. We also record our impressions and user experiences when testing the software. Easy-to-use graphical user interfaces give us a better experience, which leads to better scores.

@@

\item \textbf{Reusability} We count the total number of code files for each project. Projects with a large number of components provide more choices to reuse. Furthermore, well-modularized code, which tends to have smaller parts in separated files, is typically easier to reuse. Thus, we consider the projects with more code files to be more reusable. We use \textit{GitStats} as a tool to count the number of text-based files for all projects, and consider the projects with more text-based files to also have more code files. We also decide that the projects with API documentation can deliver better \textit{Reusability}.

@@

\item \textbf{Visibility/Transparency} To measure this quality, we check the existing documents to find out whether the software development process and current status of a project are visible and transparent. We examine the development process, current status, development environment, and release notes for each project. If any information is missing or poorly conveyed, the \textit{visibility/transparency} will be lower.
\end{itemize}

For some qualities, the empirical measurements also affect the score. We use tools to extract information from the source code repositories. For projects held on GitHub, we manually collect additional metrics, such as the stars of the GitHub repository, and the numbers of open and closed pull requests. Section \ref{sec_empirical_measurements} presents more details about the empirical measurements.

@@

We use two command-line tools for the empirical measurements. One is \textit{GitStats} that generates statistics for git repositories and displays outputs in the form of web pages \cite{Gieniusz2019}; the other one is Sloc Cloc and Code (as known as \textit{scc}) \cite{Boyter2021}, aiming to count the lines of code, comments, etc.

@@

Additionally, we manually collect information for projects held on GitHub, such as the numbers of stars, forks, people watching this repository, open pull requests, closed pull requests, and the number of months a repository has been on GitHub. A git repository can have a creation date much earlier than the first day on GitHub. For example, the developers created the git repository of \textit{3D Slicer} in 2002, but did not upload a copy of it to GitHub until 2020. We get the creation date of the GitHub copy by using API \textit{https://api.github.com/repos/{:owner}/{:repository}} (e.g., \hyperlink{https://api.github.com/repos/slicer/slicer}{https://api.github.com/repos/slicer/slicer}). In the response, the value of ``created\_at" is what we want. The number of months a repository has been on GitHub helps us understand the average change of metrics over time, e.g., the average new stars per month.

@@

\subsection{Technical Details}
\label{sec_technical_details}
To test the software on a ``clean'' system, we create a new virtual machine (VM) for each software and only install the necessary dependencies before measuring. We make all 30 VMs on the same computer, one at a time, and destroy them after measuring.

@@

The interviews are semi-structured based on the question list; we ask follow-up questions when necessary. Based on our experience, the interviewees usually bring up some exciting ideas that we did not expect, and it is worth expanding on these topics.

@@

Ideally, we select projects after the grading measurements and prefer the ones with higher overall scores. However, if we do not find enough participants, we reach all teams on the list. As mentioned in Section  \ref{sec_apply_to_mi_interviews}, when we applied this process to the MI domain, we eventually contacted all teams.

@@

\subsection{Domain Selection}
Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the sub-group of software with the Visualization function shown in Figure \ref{fig_mi_functions}. We also included Dr. Michael Noseworthy, a professor of Electrical and Computer Engineering at McMaster University, Co-Director of the McMaster School of Biomedical Engineering, and Director of Medical Imaging Physics and Engineering at St. Joseph’s Healthcare, and some of his students as the MI domain experts in our team.

\subsection{Software Product Selection}
\label{sec_mi_software_selection}
By using the method in Section \ref{sec_identify_software_candidates}, we identified 48 MI software projects as the candidates from publications \cite{Bjorn2017} \cite{Bruhschwein2019} \cite{Haak2015}, online articles related to the domain \cite{Emms2019} \cite{Hasan2020} \cite{Mu2019}, forum discussions related to the domain \cite{Samala2014}, etc. Appendix \ref{ap_list_before_filtering} shows all 48 software packages.

@@

\begin{enumerate}
\item Among them, there were eight that we could not find their source code, such as \textit{MicroDicom}, \textit{Aliza}, and \textit{jivex}. These packages are likely to be freeware defined in Section \ref{sec_freeware} and not OSS. So following guidelines in Section \ref{sec_filter_software_list} we removed them from the list.

\item Next, we focused on the MI software providing Visualization functions, as described in Section \ref{sec_scope}. Seven of the software on the list were Tool Kits or libraries for other software to use as dependencies, but not for end-users to view medical images, such as \textit{VTK}, \textit{ITK}, and \textit{dcm4che}; another three were PACS. We also eliminated these from the list.

@@

Following the process in Section \ref{sec_vet_software_list}, our domain experts provided a list of top software that contains 12 software products (Table \ref{tab_top_software_experts}). We compared two lists and found six common ones.

@@

Six software packages on the domain experts' list were not on our filtered list. We believed their primary function was Analysis mentioned in Section \ref{sec_scope}. Thus, we did not include them in our final list.

After vetting our filtered list, the domain experts believed it was reasonable and did not identify any problem. Thus, as shown in Appendix \ref{ap_list_before_filtering}, eventually, we had 29 software products on the final list.

@@

\subsection{Interviews}
\label{sec_apply_to_mi_interviews}
We received ethics clearance from the McMaster University Research Ethics Board (Appendix \ref{ap_ethics}). Going through the interview process in Section \ref{sec_interview_methods}, we contacted all of the 29 teams. As a result, developers/architects from 8 teams have participated in our interviews so far.
